N-dimensional Tic Tac Toe, and Adventure in Modules

### 2017-05-12 paper/paper.tex
Adding more to section 3

@@

>>>>

  Our project initially began as a pokemon simulator - but early on we realized
  that we could make better use of the SML module system by approaching the
  problem of simulating player-based games in a more abstract general way.
  By doing so we could define the basic notion of what a game simulation requires
  and isolate a pattern to follow for any number of games that fit this
  model.
  A game would then be a specific implementation - in our case
  \textit{Tic-tac-toe} - that used this pattern.

@@

  Our project is separated between the code that describes the game simulation
  and the code that uses this to make a specific \textit{Tic-tac-toe} implementation.
  The game simulation is located in the \texttt{game.sml} file. Likewise, the
  code for the \textit{Tic-tac-toe} implementation is located in
  \texttt{tictactoe.sml} and uses modules from \texttt{matrix.sml}.

  As we touched on before - the notion of a game is generalized in the
  \texttt{game.sml} file. This defines the modules to run a game.
  The general pattern for a game under our model consists of three purposely
  isolated pieces.
  These are \textit{State}, \textit{Actions}, and \textit{Agents}.
  These are then wrapped together with a functor. The idea is that any game
  consists of a state, a set of actions on that state, and an agents that take
  actions for a state. A specific implementation of a game would use the
  relationship between these three general pieces to define a runnable game.

  Our implementation of \textit{Tic-tac-toe} uses this game model to operate and
  is primarily defined within \texttt{tictactoe.sml}.
  Here we have two signatures - one that extends state (the \texttt{STATE}
  signature from \texttt{game.sml}) for \textit{Tic-tac-toe}
  called \texttt{TTTSTATE} and another that does the same with action called
  \texttt{TTTACTION} - we don't extend the \texttt{AGENT} signature specifically.

  There are many module structures instantiated here for the various kinds of
  state, actions and agents that we eventually want to use -
  such as \texttt{TttState} and \texttt{TttAction} for instance.
  These are bound to functors like \texttt{TttStateFn} which takes
  a module implementing a square matrix module (\texttt{SQUAREMATRIX})
  and returns a module that implements \texttt{TTTSTATE}.

  The functor \texttt{TttActionFn} (used by modules structures like
  \texttt{TttAction} and \texttt{Ttt3DAction}) takes a module that implements
  \texttt{TTTSTATE} and gives us a module implementing \texttt{TTTACTION}.

  The idea being that we created specific modules structures
  (like \texttt{TttState}) for different
  cases of actions and states that may occur in various kinds of
  \textit{Tic-tac-toe} games. We then described functors
  which linked these structures to the functions meant for that specific use.
  When provided with the correct input module these functors will give us
  modules that implement that portion of the game pattern - which we then use
  with another structure and another functor for the next modular piece of the
  game.
  % ugh I should probably rewrite that last paragraph
